Uniformly Ergodic Data-Augmented MCMC for Fitting the General Stochastic Epidemic Model to Incidence Data

### 2021-12-14 Manuscripts/Article/Article.tex

	\begin{figure}
		\centering
		\begin{subfigure}[b]{0.49\textwidth}
			\centering
			\includegraphics[width=0.45\textwidth]{E6_no_burn_beta_tp_joint.jpg}\quad
			\includegraphics[width=0.45\textwidth]{E6_burn_beta_acf_joint.jpg}
			\caption{DA-MCMC}
			\label{fig:E6_no_burn_beta_tp_joint}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.49\textwidth}
			\centering
			\includegraphics[width=0.49\textwidth]{E6_no_burn_beta_tp_single.jpg}
			\includegraphics[width=0.49\textwidth]{E6_burn_beta_acf_single.jpg}
			\caption{SSU DA-MCMC}
			\label{fig:E6_no_burn_beta_tp_single}
		\end{subfigure}
		\caption{Traceplots and auto-correlation functions of the proposed DA-MCMC and the SSU DA-MCMC for $\beta$.}
		\label{fig:E6}
	\end{figure}

@@

	\begin{figure}
		\centering
		\begin{subfigure}[b]{0.45\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E5_gamma_hist}
			\caption{Histogram of $\gamma$}
			\label{fig:E5_gamma_hist}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.49\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E5_gamma_tp}
			\caption{Posterior density of $R_0$.}
			\label{fig:density_R0}
		\end{subfigure}
		\caption{Marginal posterior distribution of $\gamma$ and its auto-correlation function for the Gu\'eck\'edou prefecture.}
		\label{fig:ebola}
	\end{figure}

>>>>

	\begin{figure}
		\centering
		\begin{subfigure}[b]{0.49\textwidth}
			\centering
			\includegraphics[width=0.49\textwidth]{E6_no_burn_beta_tp_joint.jpg}
			\includegraphics[width=0.49\textwidth]{E6_burn_beta_acf_joint.jpg}
			\caption{DA-MCMC}
			\label{fig:E6_no_burn_beta_tp_joint}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.49\textwidth}
			\centering
			\includegraphics[width=0.49\textwidth]{E6_no_burn_beta_tp_single.jpg}
			\includegraphics[width=0.49\textwidth]{E6_burn_beta_acf_single.jpg}
			\caption{SSU DA-MCMC}
			\label{fig:E6_no_burn_beta_tp_single}
		\end{subfigure}
		\caption{Traceplots and auto-correlation functions of the proposed DA-MCMC and the SSU DA-MCMC for $\beta$.}
		\label{fig:E6}
	\end{figure}

@@

	\begin{figure}
		\centering
		\begin{subfigure}[b]{0.45\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E5_expected_infection_length_hist}
			\caption{Posterior distribution of the expected infection length}
			\label{fig:E5_gamma_hist}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.49\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E5_expected_infection_length_tp}
			\caption{Traceplot.}
			\label{fig:density_R0}
		\end{subfigure}
		\caption{Marginal posterior distribution of $\gamma$ and its auto-correlation function for the Gu\'eck\'edou prefecture.}
		\label{fig:ebola}
	\end{figure}
